---
title: "Simulation Results: Analysis"
author: "M.Kamenetsky"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true # table of content true
    toc_depth: 4
---


Update 2024-10-17: updated sims including new WQS methods

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = FALSE)
library(tidyverse)
library(ggcorrplot)
library(kableExtra)
library(qgcomp)
library(gWQS)

# table one
library(tableone)
library(gt)
library(glmnet)
library(data.table)
library(ggh4x)
library(patchwork)
library(gt)
library(gtsummary)
`%ni%` <- Negate(`%in%`)
```

# FUNCTIONS

```{r}
makeplot1 <- function(dat, x, filterstring, mse=TRUE, titlestring, xlabstring, ylabstring){
  if(mse==TRUE){
    dat %>%
      dplyr::filter(type %in% c(filterstring)) %>%
      pivot_longer(cols=c(`Positive Effect`, `Negative Effect`), names_to = "posneg", values_to = "mse")%>% 
      pivot_longer(cols=c(biaspos,biasneg), names_to = "posneg2", values_to = "bias") %>%
      group_by(type, name.x,N, jointpos, jointneg, Nexposures, Nexposures0, posneg, posneg2, corr, imbalance, missing) %>%
      dplyr::summarize(mean_mse = mean(mse),
                mean_bias = mean(bias)) %>% 
      filter((posneg=="Negative Effect" & posneg2=="biasneg") | (posneg=="Positive Effect" & posneg2=="biaspos")) %>%
      mutate(name.x2 = name.x) %>%
      mutate(name.x = if_else( name.x2=="QGC: A Priori", "QGCAP",
                               if_else(name.x2 == "QGC: Enet", "QGCEN", name.x2))) %>% 
      ggplot() +
      geom_line(aes(y=sqrt(mean_mse), x=.data[[x]], group=name.x, color=name.x), size=2) +
      geom_point(aes(y=sqrt(mean_mse), x=.data[[x]], shape=name.x), size=3) +
      scale_shape_manual(values=1:9)+
      facet_grid(.~posneg) + theme_bw()+ ggtitle(titlestring) + xlab(xlabstring)+ylab(ylabstring) + theme(legend.position = "bottom",legend.title = element_blank())+
      scale_color_manual(values=mycols) 
  }else{
    scales <- list(
      scale_y_continuous(),
      scale_y_reverse()
    )
    #browser()
    dat %>%
      dplyr::filter(type %in% c(filterstring)) %>%
      pivot_longer(cols=c(`Positive Effect`, `Negative Effect`), names_to = "posneg", values_to = "mse")%>%
      pivot_longer(cols=c(biaspos,biasneg), names_to = "posneg2", values_to = "bias") %>%
      group_by(type, name.x,N, jointpos, jointneg, Nexposures, Nexposures0, posneg, posneg2,corr, imbalance, missing) %>%
      dplyr::summarize(mean_mse = mean(mse),
                mean_bias = mean(bias)) %>%
      filter((posneg=="Negative Effect" & posneg2=="biasneg") | (posneg=="Positive Effect" & posneg2=="biaspos")) %>%
      # dplyr::mutate(biasposneg2 = recode(posneg2, 
      #                             "biasneg" = "Negative Effect",
      #                             "biaspos" = "Positive Effect")) %>%
     dplyr::mutate(name.x2 = name.x) %>%
    dplyr::mutate(name.x = if_else( name.x2=="QGC: A Priori", "QGCAP",
                               if_else(name.x2 == "QGC: Enet", "QGCEN", name.x2))) %>% 
      
      ggplot() +
      geom_line(aes(y=mean_bias, x=.data[[x]], group=name.x, color=name.x), size=2) +
      geom_point(aes(y=mean_bias, x=.data[[x]], shape=name.x), size=3) +
      facet_wrap(.~posneg) +
       scale_shape_manual(values=1:9)+
      theme_bw()+ ggtitle(titlestring) + xlab(xlabstring)+ylab(ylabstring) + theme(legend.position = "bottom",legend.title = element_blank())+
      scale_color_manual(values=mycols) +
      ylim(-0.3, 0.3)
  }
}

datasummary1 <- function(dat, x, filterstring, mse=TRUE){
      outdat <- dat %>%
      dplyr::filter(type %in% c(filterstring)) %>%
      pivot_longer(cols=c(`Positive Effect`, `Negative Effect`), names_to = "posneg", values_to = "mse")%>%
      pivot_longer(cols=c(biaspos,biasneg), names_to = "posneg2", values_to = "bias") %>%
      group_by(type, name.x,N, jointpos, jointneg, Nexposures, Nexposures0, posneg, posneg2, corr, imbalance, missing) %>%
      dplyr::summarize(mean_mse = mean(mse),
                mean_bias = mean(bias)) 
      return(outdat)
}


```


```{r}
mycols <- c("#000000", "#E69F00", "#56B4E9", "#009E73", 
                       "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#999999")
```


# Prep data  
  
```{r}
# main <- read.csv("../../Results/r1/main_simpartialeffects_20241028.csv") %>%
main <- read.csv("../../Results/r1/main_simpartialeffects_20241108.csv") %>%
  filter(type != "type") %>%
  mutate(value = as.numeric(value),
         N = as.numeric(N),
         Nexposures = as.numeric(Nexposures),
         Nexposures0 = as.numeric(Nexposures0),
         bias = as.numeric(bias),
         jointpos = as.numeric(jointpos),
         jointneg = as.numeric(jointneg)) %>%
  mutate(sumpartialsTRUTH = jointpos + jointneg)

```



```{r}
datoverall <- main %>%
  dplyr::rename(simID = iter) %>%
  filter(name=="Overall (Joint Effect)") %>%
  pivot_wider(id_cols = c(simID, name, type),names_from = posneg, values_from = value)


  

mainA <- main %>%
  dplyr::rename(simID = iter) %>%
  filter(name!="Overall (Joint Effect)") %>%
  pivot_wider(id_cols = c(simID, name, type, N,jointpos, jointneg, sumpartialsTRUTH, Nexposures, Nexposures0),names_from = posneg, values_from = c(value, bias)) %>%
  dplyr::rename(poseffect = `value_Positive Effect`,
         negeffect = `value_Negative Effect`,
         biaspos = `bias_Positive Effect`,
         biasneg = `bias_Negative Effect`) %>%
  mutate(sumjointeffect = poseffect+ negeffect) %>%
  group_by(type,name) %>%
  dplyr::mutate(countn = dplyr::n()) %>%
  dplyr::mutate(`Positive Effect`  =  ((poseffect - jointpos)^2)/countn,
         `Negative Effect`  =  ((negeffect - jointneg)^2)/countn)

mainB <- merge(mainA, datoverall, by=c("simID", "type")) %>%
  dplyr::mutate(corr = ifelse(type=="base0 hicorr Exp", 0.9,
                       ifelse(type=="base0 medcorr Exp", 0.6,
                              ifelse(type=="base0 smallcorr Exp", 0.1,
                                     ifelse(type=="base0", 0,NA))))) %>%
  dplyr::mutate(imbalance = ifelse(type=="base0 small imbalance", "Small",
                       ifelse(type=="base0 med imbalance", "Medium",
                              ifelse(type=="base0 large imbalance", "Large", "No Imbalance")))) %>%
  dplyr::mutate(imbalance = fct_relevel(imbalance, c("No Imbalance","Small","Medium", "Large"))) %>% 
  dplyr::mutate(missing = ifelse(type=="base0 missingvars", "Missing Positive Exposure", "No Missing Exposures")) %>%
    dplyr::mutate(missing = fct_relevel(missing, c("No Missing Exposures", "Missing Positive Exposure"))) %>% 
  filter(name.x %ni% c("QGC: enet + X-fit", "QGC: X-fit")) %>%
  dplyr::mutate(name0 = name.x) %>%
  dplyr::mutate(name.x = dplyr::recode(name.x, 
                         "QGC: A Priori" = "QGCAP",
                         "QGC: enet" = "QGCEN")) %>% 
  dplyr::mutate(Nexposures_all = Nexposures) %>%
  dplyr::mutate(Nexposures = dplyr::recode(Nexposures, 
                             `3` = 1,
                             `6`= 4,
                             `10` = 8)) %>%
  dplyr::mutate(sum_avgbias = biaspos+biasneg) %>%
  ungroup()

main_meanjoint <- mainB %>%
  group_by(type, name.x,N) %>% 
  dplyr::summarize(meansumjoint = mean(sumjointeffect),
            meanoverall = mean(`Joint Effect`),
            n = n(),
            sd=sd(sumjointeffect),
            se = sd/sqrt(n))


main_oc <- 
  main %>%
  pivot_longer(cols=starts_with("joint"), 
               names_to = "posneg2",
               values_to = "partialeffect") %>% 
    dplyr::filter((posneg=="Negative Effect" & posneg2=="jointneg") | (posneg=="Positive Effect" & posneg2=="jointpos")) %>% 
    dplyr::mutate(partialeffect = as.numeric(partialeffect)) %>%
  dplyr::mutate(pediff = value-partialeffect,
         bdiff = bias - 0) %>%
  dplyr::mutate(maen=abs(pediff),
         msen = pediff^2,
         bmaen = abs(bdiff),
         bmsen = bdiff^2) %>%
   group_by(type, posneg, name) %>%
  dplyr::mutate(countn = n()) %>% 
 dplyr::mutate(pemae=sum(maen)/countn,
         pemse=sum(msen)/countn,
         bmae = sum(bmaen)/countn,
         bmse = sum(bmsen)/countn) %>%
  ungroup() %>%
  dplyr::mutate(type2=type)%>%
  tidyr::separate(type2, into=c("a","b"), sep="\\s")%>%
  dplyr::mutate(base0 = ifelse(a=="base0",1,0)) %>%
  dplyr::select(-c(a,b))



  
```
  
  
  
# Sample Size 

## Base Case

```{r}


(p_samplesize_mse <- makeplot1(dat=mainB,x="N", filterstring = c("base0","base0 bigN", "base0 biggerN", "base0 smallN"),
          mse=TRUE, titlestring = "Sample Size", 
          xlabstring = "Sample Size, N", 
          ylabstring = "RMSE (higher is worse)")) 


(p_samplesize_bias <- makeplot1(dat = mainB,x="N", filterstring = c("base0","base0 bigN", "base0 biggerN", "base0 smallN"),
          mse=FALSE, titlestring = "Sample Size" , 
          xlabstring = "Sample Size, N", 
          ylabstring = "Average Bias (zero is best)") + 
      ylim(-0.2, 0.2))



```


## Values for Manuscript

```{r}

#MSE
outsamp_mse <- datasummary1(mainB, x= "type",filterstring = c("base0","base0 bigN", "base0 biggerN", "base0 smallN"),
          mse=TRUE) %>%
  filter((posneg=="Negative Effect" & posneg2=="biasneg") | (posneg=="Positive Effect" & posneg2=="biaspos"))
outsamp_mse


#average bias
outsamp_bias <- datasummary1(mainB, x= "type",filterstring = c("base0","base0 bigN", "base0 biggerN", "base0 smallN"),
          mse=FALSE) %>%
  filter((posneg=="Negative Effect" & posneg2=="biasneg") | (posneg=="Positive Effect" & posneg2=="biaspos"))
outsamp_bias


```



   
   

# Spread in exposures  

## Base Case

```{r}

(p_spread_mse <- makeplot1(dat = mainB, x= "Nexposures",filterstring = c("base0 spread4", "base0 spread1", "base0 spread8"),
          mse=TRUE, titlestring = "Spreading the Negative Partial Effect\nOver More Exposures", 
          xlabstring = "Number of Negative Exposures", 
          ylabstring = "RMSE (higher is worse)"))
(p_spread_bias <- makeplot1(dat = mainB, x= "Nexposures",filterstring = c("base0 spread4", "base0 spread1", "base0 spread8"),
          mse=FALSE, titlestring = "Spreading the Partial Effect\nOver More Exposures", 
          xlabstring = "Number of Negative Exposures", 
          ylabstring = "Average Bias (zero is best)"))



```






## Values for Manuscript

```{r}

#MSE
outspread_mse <- datasummary1(mainB, x= "type",filterstring = c("base0 spread4", "base0 spread1", "base0 spread8"),
          mse=TRUE) %>%
  filter((posneg=="Negative Effect" & posneg2=="biasneg") | (posneg=="Positive Effect" & posneg2=="biaspos"))
outspread_mse



#Average Bias
outspread_bias <- datasummary1(mainB, x= "type",filterstring = c("base0 spread4", "base0 spread1", "base0 spread8"),
          mse=FALSE) %>%
  filter((posneg=="Negative Effect" & posneg2=="biasneg") | (posneg=="Positive Effect" & posneg2=="biaspos"))
outspread_bias

```






# Hi/Med/Low Correlation in Exposures

## Base Case

```{r}

(p_corr_mse <-makeplot1(dat = mainB, x= "corr",filterstring = c("base0 hicorr Exp", "base0 medcorr Exp", "base0 smallcorr Exp","base0"),
          mse=TRUE, titlestring = "Correlated Exposures", 
          xlabstring = "Correlation", 
          ylabstring = "RMSE (higher is worse)"))
(p_corr_bias <- makeplot1(dat = mainB, x= "corr",filterstring = c("base0 hicorr Exp", "base0 medcorr Exp", "base0 smallcorr Exp","base0"),
          mse=FALSE, titlestring = "Correlated Exposures", 
          xlabstring = "Correlation", 
          ylabstring = "Average Bias (zero is best)"))




```

## Values for Manuscript

```{r}

#MSE
outcorr_mse <- datasummary1(mainB, x= "type",filterstring = c("base0 hicorr Exp", "base0 medcorr Exp", "base0 smallcorr Exp","base0"),
          mse=TRUE) %>%
  filter((posneg=="Negative Effect" & posneg2=="biasneg") | (posneg=="Positive Effect" & posneg2=="biaspos"))
outcorr_mse


#Average Bias
outcorr_bias <- datasummary1(mainB, x= "type",filterstring = c("base0 hicorr Exp", "base0 medcorr Exp", "base0 smallcorr Exp","base0"),
          mse=FALSE) %>%
  filter((posneg=="Negative Effect" & posneg2=="biasneg") | (posneg=="Positive Effect" & posneg2=="biaspos"))
outcorr_bias 
```




# Small/medium/large imbalance in partial effects

## Base Case


```{r}

(p_imbalance_mse <- makeplot1(dat = mainB, x= "imbalance",filterstring = c("base0","base0 small imbalance", "base0 med imbalance", "base0 large imbalance"),
          mse=TRUE, titlestring = "Imbalance in Positive Effect", 
          xlabstring = "Imbalance", 
          ylabstring = "RMSE (higher is worse)") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))
  

(p_imbalance_bias <- makeplot1(dat = mainB, x= "imbalance",filterstring = c("base0","base0 small imbalance", "base0 med imbalance", "base0 large imbalance"),
          mse=FALSE, titlestring = "Imbalance in Positive Effect", 
          xlabstring = "Imbalance", 
          ylabstring = "Average Bias (zero is best)")+
          theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)))




```



## Values for Manuscript

```{r}

#MSE
outimbalance_mse <- datasummary1(mainB, x= "type",filterstring = c("base0","base0 small imbalance", "base0 med imbalance", "base0 large imbalance"),
          mse=TRUE) %>%
  filter((posneg=="Negative Effect" & posneg2=="biasneg") | (posneg=="Positive Effect" & posneg2=="biaspos"))
outimbalance_mse



#Average Bias
outimbalance_bias <- datasummary1(mainB, x= "type",filterstring = c("base0","base0 small imbalance", "base0 med imbalance", "base0 large imbalance"),
          mse=FALSE) %>%
  filter((posneg=="Negative Effect" & posneg2=="biasneg") | (posneg=="Positive Effect" & posneg2=="biaspos"))
outimbalance_bias


```




# Combine Plots (Manuscript Figures 1 and 2)


```{r}
library(patchwork)

p_corr_mse + p_samplesize_mse +  p_spread_mse + p_imbalance_mse + plot_layout(ncol=2) + plot_annotation(tag_levels = "A", title="Comparison of Root Mean Squared Error (RMSE) Across Methods Estimating Partial Effects")
ggsave(filename = "../../Manuscript/EHP/Resubmission/figures/Figure1.pdf", width = 10, height = 10, units = "in")



p_corr_bias + p_samplesize_bias +  p_spread_bias + p_imbalance_bias+ plot_layout(ncol=2) + plot_annotation(tag_levels = "A", title="Comparison of Average Bias Across Methods Estimating Partial Effects")
ggsave(filename = "../../Manuscript/EHP/Resubmission/figures/Figure2.pdf", width = 10, height = 10, units = "in")



```

# Create Tables

## Sample size

```{r}


tab <-  mainB %>%
      filter(type %in% c("base0","base0 bigN", "base0 biggerN", "base0 smallN")) %>%
      pivot_longer(cols=c(`Positive Effect`, `Negative Effect`), names_to = "posneg", values_to = "mse")%>%
      pivot_longer(cols=c(biaspos,biasneg), names_to = "posneg2", values_to = "bias") %>%
      group_by(type, name.x,N, jointpos, jointneg, Nexposures, Nexposures0, posneg, posneg2, corr, imbalance) %>%
      summarize(mean_mse = mean(mse),
                mean_bias = mean(bias), .groups="drop") %>% 
      filter((posneg=="Negative Effect" & posneg2=="biasneg") | (posneg=="Positive Effect" & posneg2=="biaspos")) %>%
  ungroup() %>%
  dplyr::select(-c(type, jointpos, jointneg, Nexposures, Nexposures0, posneg2, corr, imbalance)) %>%
  pivot_wider(names_from = "posneg", values_from = c("mean_mse", "mean_bias"))

tab %>%
   mutate(name = if_else( name.x=="QGC: A Priori", "QGCAP",
                               if_else(name.x == "QGC: Enet", "QGCEN", name.x))) %>%
  relocate(name) %>%
  dplyr::select(-name.x) %>%
  arrange(N, name) %>%
  mutate(`mean_mse_Negative Effect` = sqrt(`mean_mse_Negative Effect`),
         `mean_mse_Positive Effect` = sqrt(`mean_mse_Positive Effect`)) %>%
  gt() %>%
  fmt_number(columns = 3:6,n_sigfig = 3) %>%
  fmt_scientific(columns = 5:6, n_sigfig = 3) %>%
  cols_label(name="Method",
             "mean_mse_Negative Effect" = "Negative Effect",
             "mean_mse_Positive Effect" = "Positive Effect",
             "mean_bias_Negative Effect" = "Negative Effect",
             "mean_bias_Positive Effect" = "Positive Effect") %>%
  tab_spanner(label="RMSE", columns=3:4, id=1) %>%
  tab_spanner(label="Bias", columns=5:6, id=2) %>%
  tab_header(title="Simulation Results: Sample Size")%>%
  gt::gtsave(., "../../Manuscript/EHP/Resubmission/tables/sim_samplesize.rtf")


```

## Spread

```{r}
tab <-  mainB %>%
      filter(type %in% c("base0 spread4", "base0 spread1", "base0 spread8")) %>%
      pivot_longer(cols=c(`Positive Effect`, `Negative Effect`), names_to = "posneg", values_to = "mse")%>%
      pivot_longer(cols=c(biaspos,biasneg), names_to = "posneg2", values_to = "bias") %>%
      group_by(type, name.x,N, jointpos, jointneg, Nexposures, Nexposures0, posneg, posneg2, corr, imbalance) %>%
      summarize(mean_mse = mean(mse),
                mean_bias = mean(bias), .groups="drop") %>% 
      filter((posneg=="Negative Effect" & posneg2=="biasneg") | (posneg=="Positive Effect" & posneg2=="biaspos")) %>%
  ungroup() %>%
  dplyr::select(-c(type, jointpos, jointneg, N, Nexposures0, posneg2, corr, imbalance)) %>%
  pivot_wider(names_from = "posneg", values_from = c("mean_mse", "mean_bias"))

tab %>%
 mutate(name = if_else( name.x=="QGC: A Priori", "QGCAP",
                               if_else(name.x == "QGC: Enet", "QGCEN", name.x))) %>%
    mutate(`mean_mse_Negative Effect` = sqrt(`mean_mse_Negative Effect`),
         `mean_mse_Positive Effect` = sqrt(`mean_mse_Positive Effect`)) %>%
  relocate(name) %>%
  dplyr::select(-name.x) %>%
  arrange(Nexposures, name) %>%
  gt() %>%
    fmt_number(columns = 3:6,n_sigfig = 3) %>%
  fmt_scientific(columns = 5:6, n_sigfig = 3) %>%
  cols_label(name="Method",
             Nexposures = "Number of Exposures",
             "mean_mse_Negative Effect" = "Negative Effect",
             "mean_mse_Positive Effect" = "Positive Effect",
             "mean_bias_Negative Effect" = "Negative Effect",
             "mean_bias_Positive Effect" = "Positive Effect") %>%
  tab_spanner(label="RMSE", columns=3:4, id=1) %>%
  tab_spanner(label="Bias", columns=5:6, id=2) %>%
  tab_header(title="Simulation Results: Spread in Negative Effect Across Exposures")  %>%
  gt::gtsave(., "../../Manuscript/EHP/Resubmission/tables/sim_spread.rtf")
```

## Correlation

```{r}
tab <-  mainB %>%
      filter(type %in% c("base0 hicorr Exp", "base0 medcorr Exp", "base0 smallcorr Exp","base0")) %>%
      pivot_longer(cols=c(`Positive Effect`, `Negative Effect`), names_to = "posneg", values_to = "mse")%>%
      pivot_longer(cols=c(biaspos,biasneg), names_to = "posneg2", values_to = "bias") %>%
      group_by(type, name.x,N, jointpos, jointneg, Nexposures, Nexposures0, posneg, posneg2, corr, imbalance) %>%
      summarize(mean_mse = mean(mse),
                mean_bias = mean(bias), .groups="drop") %>% 
      filter((posneg=="Negative Effect" & posneg2=="biasneg") | (posneg=="Positive Effect" & posneg2=="biaspos")) %>%
  ungroup() %>%
  dplyr::select(-c(type, jointpos, jointneg, Nexposures, N, Nexposures0, posneg2,  imbalance)) %>%
  pivot_wider(names_from = "posneg", values_from = c("mean_mse", "mean_bias"))

tab %>%
 mutate(name = if_else( name.x=="QGC: A Priori", "QGCAP",
                               if_else(name.x == "QGC: Enet", "QGCEN", name.x))) %>%
    mutate(`mean_mse_Negative Effect` = sqrt(`mean_mse_Negative Effect`),
         `mean_mse_Positive Effect` = sqrt(`mean_mse_Positive Effect`)) %>%
  relocate(name) %>%
  dplyr::select(-name.x) %>%
  arrange(corr, name) %>%
  gt() %>%
    fmt_number(columns = 3:6,n_sigfig = 3) %>%
  fmt_scientific(columns = 5:6, n_sigfig = 3) %>%
  cols_label(name="Method",
             corr = "Correlation",
             "mean_mse_Negative Effect" = "Negative Effect",
             "mean_mse_Positive Effect" = "Positive Effect",
             "mean_bias_Negative Effect" = "Negative Effect",
             "mean_bias_Positive Effect" = "Positive Effect") %>%
  tab_spanner(label="MSE", columns=3:4, id=1) %>%
  tab_spanner(label="Bias", columns=5:6, id=2) %>%
  tab_header(title="Simulation Results: Correlation Among Exposures") %>%
  gt::gtsave(., "../../Manuscript/EHP/Resubmission/tables/sim_correlation.rtf")
```



## Imbalance

```{r}
tab <-  mainB %>%
      filter(type %in% c("base0","base0 small imbalance", "base0 med imbalance", "base0 large imbalance")) %>%
      pivot_longer(cols=c(`Positive Effect`, `Negative Effect`), names_to = "posneg", values_to = "mse")%>%
      pivot_longer(cols=c(biaspos,biasneg), names_to = "posneg2", values_to = "bias") %>%
      group_by(type, name.x,N, jointpos, jointneg, Nexposures, Nexposures0, posneg, posneg2, corr, imbalance) %>%
      summarize(mean_mse = mean(mse),
                mean_bias = mean(bias), .groups="drop") %>% 
      filter((posneg=="Negative Effect" & posneg2=="biasneg") | (posneg=="Positive Effect" & posneg2=="biaspos")) %>%
  ungroup() %>%
  dplyr::select(-c(type, jointpos, jointneg, Nexposures, N, Nexposures0, posneg2,  corr)) %>%
  pivot_wider(names_from = "posneg", values_from = c("mean_mse", "mean_bias"))

tab %>%
 mutate(name = if_else( name.x=="QGC: A Priori", "QGCAP",
                               if_else(name.x == "QGC: Enet", "QGCEN", name.x))) %>%
    mutate(`mean_mse_Negative Effect` = sqrt(`mean_mse_Negative Effect`),
         `mean_mse_Positive Effect` = sqrt(`mean_mse_Positive Effect`)) %>%

  relocate(name) %>%
  dplyr::select(-name.x) %>%
  arrange(imbalance, name) %>%
  gt() %>%
    fmt_number(columns = 3:6,n_sigfig = 3) %>%
  fmt_scientific(columns = 5:6, n_sigfig = 3) %>%
  cols_label(name="Method",
             imbalance= "Imbalance",
             "mean_mse_Negative Effect" = "Negative Effect",
             "mean_mse_Positive Effect" = "Positive Effect",
             "mean_bias_Negative Effect" = "Negative Effect",
             "mean_bias_Positive Effect" = "Positive Effect") %>%
  tab_spanner(label="MSE", columns=3:4, id=1) %>%
  tab_spanner(label="Bias", columns=5:6, id=2) %>%
  tab_header(title="Simulation Results: Imbalance in Effects") %>%
  gt::gtsave(., "../../Manuscript/EHP/Resubmission/tables/sim_imbalance.rtf")
```

